Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-25 doc/PRF2022/PRF_main.tex
yny3

For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculated the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area achieves a
steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (data not shown). 
In other words, the fluid-structure interactions of JPs give rise to 
non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
This result is similar to the non-monotonic pressure-flow rate relation in the clogging of
spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.

>>>>

For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
JP vesicle as the inner leaflet of JPs move clockwise along the boundary
faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
there is only one TG cell inside the JP vesicle and the JPs in the
bilayer tank-tread in the counter-clockwise direction (Figure
\ref{fig:PramChange}(b)--(e)). 
%
Finally, we calculated the vesicle area $A$ and length $L$. As shown in
Figure~\ref{fig:PramChange}(f), the relative area achieves a
steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
$t$ for all cell sizes (data not shown). 
In other words, the fluid-structure interactions of JPs give rise to 
non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
Such dynamic pressure-flow rate relation is also found in the clogging of
spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.
